Optimal Finite Element Integration

### 2015-07-31 TOMS_Paper/assembly.tex
Start talking about coffee language

Our research has resulted in ....
... we build on our previous work~\cite{Luporini} ... and present a ... We argue that for complex, realistic forms, peak performance can be achieved only by  ... 
... also low-level optimisation ...
...also for the first time we provide a formal explanation of the math in terms of compiler theory

@@

\section{Code Generation}
\label{sec:codegen}

\begin{itemize}
\item Deficiencies of previous approaches
\item  Building block operations in coffee: 1) eliminating reuse, 2)  insights on the various tree algorithms employed
\end{itemize}

\subsection{Heuristic Optimization of Integration-dependent Expressions}
%insights that optimisation of loops outside of the multilinear nest can be tackled greedily and heuristically

>>>>

Our research has resulted in ....
... we build on our previous work~\cite{Luporini} ... and present a ... We argue that for complex, realistic forms, peak performance can be achieved only by  ... 
... also low-level optimisation ...
...also for the first time we provide a formal explanation of the math in terms of compiler theory
-  Deficiencies of previous approaches

@@

\section{Code Generation}
\label{sec:codegen}
The analysis described in Section~\ref{sec:optimal-synthesis} has been fully automated in COFFEE, the optimization system for local assembly used in Firedrake. In this section, we describe the structure of the code generation system and we comment on a set of low-level optimizations.

\subsection{Automation through the COFFEE Language}
As opposed to what happens in FFC with quadrature and tensor modes, there are no separate trunks in COFFEE handling pre-evaluation, sharing, and code motion in general: all optimizations are expressed as composition of parametric "building-block" operations. This has several advantages. Firstly, extendibility: novel transformations -- for instance, sum-factorization in spectral methods -- could ideally be expressed using the existing operators, or with small effort building on what is already available. Secondly, generality: other domains sharing properties similar to that of finite element integration (e.g., multilinear loop nests) could be optimized through the same compiler. Thirdly, robustness: the same building-block operations are exploited, and therefore stressed, by different optimization pipelines.

A non-exhaustive list of such operations includes expansion, factorization, re-association, generalized code motion. These are parametric operations. For example, one could ask to factorize only constant or only linear terms, while hoisting can be limited by imposing a constraint on the size of the temporaries. Each of these operations is implemented by suitable manipulation of the abstract syntax tree representing the integration routine.

\subsubsection{Heuristic Optimization of Integration-dependent Expressions}
As a proof-of-concept of our generality claim,
